---
title: "Control File"
author: "Brad Hughes & Alicia Kantor"
date: "December 3, 2019"
output: html_document
---
Below is the summary of our data. For additional work, reference our github:  https://github.com/akantorluc/Consulting

### Data Manipulation
```{r}
library(tidyverse)
library(reshape2)
library(dplyr)
library(readr)

long_data = dcast(melt(newData), plot + subplot ~ year + variable, fill = NA)
long_data = long_data %>% mutate(YR2016_detritusAW = ifelse(is.na(YR2016_detritusAW), 99, YR2016_detritusAW))
long_data = long_data %>% mutate(YR2017_totalVegCover = (YR2016_totalVegCover + YR2018_totalVegCover)/2, 
                                 YR2017_unVegCover = (YR2016_unVegCover + YR2018_unVegCover)/2,
                                 YR2015_detritusAW = YR2016_detritusAW,
                                 YR2015_typhaDens = YR2016_typhaDens)
long_data = long_data %>% mutate(logYR2015_detritusAW = log(YR2015_detritusAW + 1), logYR2016_detritusAW = log(YR2016_detritusAW + 1), 
                                 logYR2017_detritusAW = log(YR2017_detritusAW + 1), logYR2018_detritusAW = log(YR2018_detritusAW + 1), 
                                 logYR2015_aquatics = log(YR2015_aquatics + 1), logYR2016_aquatics = log(YR2016_aquatics + 1), 
                                 logYR2017_aquatics = log(YR2017_aquatics + 1), logYR2018_aquatics = log(YR2018_aquatics + 1))
long_data = long_data %>% mutate(YR2015_typhaBM100 = YR2015_typhaBM / 100, YR2016_typhaBM100 = YR2016_typhaBM / 100, 
                                 YR2017_typhaBM100 = YR2017_typhaBM / 100, YR2018_typhaBM100 = YR2018_typhaBM / 100)

global_data = Global_Control_Cheboygan
global_data = global_data %>% filter(year=="YR2015" | year =="YR2016" | year=="YR2017" | year=="YR2018")
global_data[5:23] = as.data.frame(lapply(global_data[5:23], as.double))
global_data = global_data %>% mutate(typhaBM100 = typhaBM/100)

global_data = global_data %>% mutate(detritusAW10 = detritusAW/10, unVegCover10 = unVegCover / 10, 
                                     waterDepth10 = waterDepth / 10, NO3_N10 = NO3_N / 10, 
                                     organic10 = organic / 10)
global_data[1:4] = as.data.frame(lapply(global_data[1:4], as.factor))
global_data$year = as.character(global_data$year)
global_data$year = parse_number(global_data$year)
```

### Data Exploration
```{r}
library(ggplot2)
ggplot(global_data, aes(x=year, y = waterDepth, colour = plot, group=plot)) + 
 geom_smooth(method = "loess", size=2, alpha=0.15) +
  theme_classic()

ggplot(global_data, aes(x=year, y = typhaBM, colour = plot, group=plot)) + 
  geom_smooth(method = "loess", size=2, alpha=0.15) +
  theme_classic()

ggplot(global_data, aes(x=year, y = detritusAW, colour = plot, group=plot)) + 
  geom_smooth(method = "loess", size=2, alpha=0.15) +
  theme_classic()

ggplot(global_data, aes(x=year, y = totalVegCover, colour = plot, group=plot)) + 
  geom_smooth(method = "loess", size=2, alpha=0.15) +
  theme_classic()

ggplot(global_data, aes(x=year, y = aquatics, colour = plot, group=plot)) + 
  geom_smooth(method = "loess", size=2, alpha=0.15) +
  theme_classic()

#RIP XXXX-2016
ggplot(global_data, aes(x=year, y = woody, colour = plot, group=plot)) + 
  geom_smooth(method = "loess", size=2, alpha=0.15) +
  theme_classic()
```

### Assumptions
```{r}
attach(Ohsowski_Control_Data)

hist(detriusAW16)

# Water
hist(waterDepth15)
hist(waterDepth16)
hist(waterDepth17)
water <- c(waterDepth15, waterDepth16, waterDepth17, waterDepth18, waterDepth19)
hist(water)

# Typha
hist(typhaBM15)
hist(typhaBM16)
hist(typhaBM17)
typ <- c(typhaBM15, typhaBM16, typhaBM17, typhaBM18)
hist(typ)

# Veg Cover
hist(totalVegCover15)
hist(totalVegCover16)
veg <- c(totalVegCover15, totalVegCover16, totalVegCover18, totalVegCover19)
hist(veg)

# Aquatics
hist(aquatics15)
hist(aquatics16)
aqu <- c(aquatics15, aquatics16, aquatics17, aquatics18)
hist(aqu)

attach(newData)
par(mfrow = c(1,1))
hist(organic) #slight right skewed, pretty normal
hist(H) #very right skewed/ zero inflated
hist(richness) #count data, right skewed?
hist(typhaDens) #normal
hist(NO3_N) #very right skewed
hist(NH4_N, breaks = 15) #slight right skewed with 1 very high outlier
hist(sedges) #really bad zero inflated but maybe useful
hist(rushes) #exclude
hist(grasses) #exclude
hist(graminoids) #normal
hist(forbs) #zero inflated (9/25)
hist(woody) #only 1 tree so exclude
hist(typCover) #normal
hist(typhaBM) #right skewed
hist(detritusAW) #right skewed with lots of zeros
hist(waterDepth) #right skewed
hist(totalVegCover) #slight right skew
hist(aquatics) #zero inflated and awful
```

### Longitudinal Piecewise SEM
```{r}
library(lavaan)

model1 <- 'Typha ~ waterDepth
          detritus ~ Typha
          TotalVegCover ~ detritus
          aquatics ~ TotalVegCover + detritus'

attach(long_data)
library(nlme)
library(piecewiseSEM)

new.modlist <- psem(
  lme(YR2016_typhaBM ~ YR2015_typhaBM + YR2015_waterDepth, random = ~1|plot, data = long_data),
  lme(YR2017_typhaBM ~ YR2016_typhaBM + YR2016_waterDepth, random = ~1|plot, data = long_data),
  lme(YR2018_typhaBM ~ YR2017_typhaBM + YR2017_waterDepth, random = ~1|plot, data = long_data),
  lme(YR2016_detritusAW ~ YR2015_typhaBM, random = ~1|plot, data = long_data),
  lme(YR2017_detritusAW ~ YR2016_detritusAW + YR2016_typhaBM, random = ~1|plot, data = long_data),
  lme(YR2018_detritusAW ~ YR2017_detritusAW + YR2017_typhaBM, random = ~1|plot, data = long_data),
  lme(YR2016_totalVegCover ~ YR2015_totalVegCover, random = ~1|plot, data = long_data),
  lme(YR2018_totalVegCover ~ YR2017_detritusAW, random = ~1|plot, data = long_data),
  lme(YR2016_aquatics ~ YR2015_aquatics + YR2015_totalVegCover, random = ~1|plot, data = long_data),
  lme(YR2017_aquatics ~ YR2016_aquatics + YR2016_totalVegCover + YR2016_detritusAW, random = ~1|plot, data = long_data),
  lme(YR2018_aquatics ~ YR2017_aquatics + YR2017_detritusAW, random = ~1|plot, data = long_data)
)
summary(new.modlist, long_data)

# accounting for relationship between same year responses since there is no covariance
new.modlist1 <- psem(
  lme(YR2016_typhaBM ~ YR2015_typhaBM + YR2015_waterDepth + YR2016_waterDepth, random = ~1|plot, data = long_data),
  lme(YR2017_typhaBM ~ YR2016_typhaBM + YR2016_waterDepth + YR2017_waterDepth, random = ~1|plot, data = long_data),
  lme(YR2018_typhaBM ~ YR2017_typhaBM + YR2017_waterDepth + YR2018_waterDepth, random = ~1|plot, data = long_data),
  lme(YR2016_detritusAW ~ YR2015_typhaBM + YR2016_typhaBM, random = ~1|plot, data = long_data),
  lme(YR2017_detritusAW ~ YR2016_detritusAW + YR2016_typhaBM + YR2017_typhaBM, random = ~1|plot, data = long_data),
  lme(YR2018_detritusAW ~ YR2017_detritusAW + YR2017_typhaBM + YR2018_typhaBM, random = ~1|plot, data = long_data),
  lme(YR2016_totalVegCover ~ YR2016_detritusAW + YR2015_totalVegCover, random = ~1|plot, data = long_data),
  lme(YR2018_totalVegCover ~ YR2017_detritusAW + YR2018_detritusAW, random = ~1|plot, data = long_data),
  lme(YR2016_aquatics ~ YR2015_aquatics + YR2015_totalVegCover + YR2016_totalVegCover, random = ~1|plot, data = long_data),
  lme(YR2017_aquatics ~ YR2016_aquatics + YR2016_totalVegCover + YR2016_detritusAW + YR2017_detritusAW, random = ~1|plot, data = long_data),
  lme(YR2018_aquatics ~ YR2017_aquatics + YR2017_detritusAW + YR2018_detritusAW + YR2018_totalVegCover, random = ~1|plot, data = long_data)
)
summary(new.modlist1, long_data)

# Adding in significant relationships
new.modlist2 <- psem(
  lme(YR2016_typhaBM ~ YR2015_typhaBM + YR2015_waterDepth + YR2016_waterDepth, random = ~1|plot, data = long_data),
  lme(YR2017_typhaBM ~ YR2016_typhaBM + YR2016_waterDepth + YR2017_waterDepth, random = ~1|plot, data = long_data),
  lme(YR2018_typhaBM ~ YR2017_typhaBM + YR2017_waterDepth + YR2018_waterDepth, random = ~1|plot, data = long_data),
  lme(YR2016_detritusAW ~ YR2015_typhaBM + YR2016_typhaBM + YR2015_waterDepth + YR2016_waterDepth, random = ~1|plot, data = long_data),
  lme(YR2017_detritusAW ~ YR2016_detritusAW + YR2016_typhaBM + YR2017_typhaBM + YR2016_waterDepth + YR2017_waterDepth, random = ~1|plot, data = long_data),
  lme(YR2018_detritusAW ~ YR2017_detritusAW + YR2017_typhaBM + YR2018_typhaBM + YR2017_waterDepth + YR2018_waterDepth, random = ~1|plot, data = long_data),
  lme(YR2016_totalVegCover ~ YR2016_detritusAW + YR2015_totalVegCover + YR2015_waterDepth + YR2016_waterDepth, random = ~1|plot, data = long_data),
  lme(YR2018_totalVegCover ~ YR2017_detritusAW + YR2018_detritusAW + YR2016_totalVegCover + YR2017_waterDepth + YR2018_waterDepth, random = ~1|plot, data = long_data),
  lme(YR2016_aquatics ~ YR2015_aquatics + YR2015_totalVegCover + YR2016_totalVegCover, random = ~1|plot, data = long_data),
  lme(YR2017_aquatics ~ YR2016_aquatics + YR2016_totalVegCover + YR2016_detritusAW + YR2017_detritusAW, random = ~1|plot, data = long_data),
  lme(YR2018_aquatics ~ YR2017_aquatics + YR2017_detritusAW + YR2018_detritusAW + YR2018_totalVegCover, random = ~1|plot, data = long_data)
)
summary(new.modlist2, long_data)

# removing unnecessary links
new.modlist2 <- psem(
  lme(YR2016_detritusAW ~ YR2015_waterDepth, random = ~1|plot, data = long_data),
  lme(YR2017_detritusAW ~ YR2016_waterDepth + YR2017_waterDepth, random = ~1|plot, data = long_data),
  lme(YR2018_detritusAW ~ YR2017_waterDepth, random = ~1|plot, data = long_data),
  lme(YR2018_totalVegCover ~ YR2018_detritusAW + YR2018_waterDepth, random = ~1|plot, data = long_data),
  lme(YR2016_aquatics ~ YR2015_aquatics, random = ~1|plot, data = long_data),
  lme(YR2017_aquatics ~ YR2015_aquatics + YR2016_detritusAW + YR2016_aquatics, random = ~1|plot, data = long_data),
  lme(YR2018_aquatics ~ YR2016_detritusAW + YR2018_detritusAW + YR2018_totalVegCover, random = ~1|plot, data = long_data)
)
summary(new.modlist2, long_data)
```

### Global SEM
```{r}
library(lavaan)

#original model by Brian also not good
mod1 <- 'typhaBM ~ waterDepth
          detritusAW ~ typhaBM
          totalVegCover ~ detritusAW
          aquatics ~ totalVegCover + detritusAW'
mod11 = sem(mod1, data = global_data, estimator="mlm")
summary(mod11)

# Good model
mod2 <- 'typhaBM100 ~ waterDepth + H + unVegCover
          graminoids ~ H
          detritusAW ~ typhaBM100 + NH4_N + waterDepth + H
          richness ~ H + NO3_N + typhaBM100 + organic
          aquatics ~ H + NO3_N + organic + waterDepth'
mod22 = sem(mod2, data = global_data, estimator="mlm")
summary(mod22, fit.measures = T)
```

### Piecewise SEM based on global mod2
```{r}
library(devtools)
library(piecewiseSEM)
library(lmerTest)
library(nlme)

#'typhaBM100 ~ waterDepth + H + unVegCover
#          graminoids ~ H
#          detritusAW ~ typhaBM100 + NH4_N + waterDepth + H
#          richness ~ H + NO3_N + typhaBM100 + organic
#          aquatics ~ H + NO3_N + organic + waterDepth'

pmod1 <- psem(
  lme(typhaBM100 ~ waterDepth + H + unVegCover, random = ~1|plot, data = global_data), 
  lme(graminoids ~ H, random = ~1|plot, data = global_data),
  lme(detritusAW ~ typhaBM100 + NH4_N + waterDepth + H, random = ~1|plot, data = global_data),
  lme(richness ~ H + NO3_N + typhaBM100 + organic, random = ~1|plot, data = global_data),
  lme(aquatics ~ H + NO3_N + organic + waterDepth, random = ~1|plot, data = global_data)
)
summary(pmod1)

# Adding in missing connections
pmod2 <- psem(
  lme(typhaBM100 ~ waterDepth + H + unVegCover, random = ~1|plot, data = global_data), 
  lme(graminoids ~ H + typhaBM100, random = ~1|plot, data = global_data),
  lme(detritusAW ~ typhaBM100 + NH4_N + waterDepth + H, random = ~1|plot, data = global_data),
  lme(richness ~ H + NO3_N + typhaBM100 + organic + graminoids, random = ~1|plot, data = global_data),
  lme(aquatics ~ H + NO3_N + organic + waterDepth + graminoids, random = ~1|plot, data = global_data)
)
summary(pmod2)

# Taking out insignificant terms
pmod3 <- psem(
  lme(typhaBM100 ~ unVegCover, random = ~1|plot, data = global_data), 
  lme(graminoids ~ H + unVegCover + waterDepth, random = ~1|plot, data = global_data),
  lme(detritusAW ~ typhaBM100 + NH4_N + waterDepth, random = ~1|plot, data = global_data),
  lme(richness ~ H + NO3_N + typhaBM100 + organic + graminoids, random = ~1|plot, data = global_data),
  lme(aquatics ~ H + NO3_N + waterDepth + graminoids, random = ~1|plot, data = global_data)
)
summary(pmod3) # 0.562

pmod4 <- psem(
  lme(typhaBM100 ~ unVegCover, random = ~1|plot, data = global_data), 
  lme(graminoids ~ H + unVegCover + waterDepth + typhaBM100, random = ~1|plot, data = global_data),
  lme(detritusAW ~ typhaBM100 + NH4_N + waterDepth, random = ~1|plot, data = global_data),
  lme(richness ~ H + NO3_N + typhaBM100 + organic + graminoids, random = ~1|plot, data = global_data),
  lme(aquatics ~ H + NO3_N + waterDepth + graminoids, random = ~1|plot, data = global_data)
)
summary(pmod4) # 0.825

# Best model = no missing terms or bad relationships. No graminoids response. 
pmod5 <- psem(
  lme(typhaBM100 ~ unVegCover + graminoids + year, random = ~1|plot, data = global_data), 
  lme(log(detritusAW+1) ~ typhaBM100 + NH4_N + waterDepth + year, random = ~1|plot, data = global_data),
  lme(richness ~ H + NO3_N + graminoids + typhaBM100 + organic + year, random = ~1|plot, data = global_data),
  lme(log(aquatics) ~ H + NO3_N + graminoids + waterDepth, random = ~1|plot, data = global_data)
)
summary(pmod5) # 0.669

# Adjusting for the loged responses
pmod6 <- psem(
  lme(typhaBM100 ~ unVegCover + graminoids, random = ~1|plot, data = global_data), 
  lme(log(detritusAW+1) ~ waterDepth + typhaBM100, random = ~1|plot, data = global_data),
  lme(richness ~ H + NO3_N + graminoids + typhaBM100 + organic, random = ~1|plot, data = global_data),
  lme(log(aquatics+1) ~ H + NO3_N + graminoids + waterDepth + typhaBM100 + richness, random = ~1|plot, data = global_data)
)
summary(pmod6) # .768


############################################################

# Adding in year - best model!!!!!!!!!!!
pmod7 <- psem(
  lme(typhaBM100 ~ unVegCover + graminoids + NO3_N + organic + year, random = ~1|plot, data = global_data), 
  lme(log(detritusAW+1) ~ waterDepth + typhaBM100, random = ~1|plot, data = global_data),
  lme(richness ~ H + NO3_N + graminoids + typhaBM100 + organic, random = ~1|plot, data = global_data),
  lme(log(aquatics+1) ~ H + NO3_N + graminoids + waterDepth + typhaBM100 + richness + year, random = ~1|plot, data = global_data)
)
summary(pmod7) # .803


### Checking model assumptions...
lmt <- glm(typhaBM100 ~ unVegCover + graminoids, data = global_data)
hist(lmt$residuals, breaks = 20)# 3 outliers so normal
plot(lmt)
par(mfrow = c(2, 2))

lmd <- glm(log(detritusAW+1) ~ typhaBM100 + NH4_N + waterDepth, data = subset(global_data, detritusAW != 99))
hist(lmd$residuals)
plot(lmd) # good enough

lmr <- glm(richness ~ H + NO3_N + graminoids + typhaBM100 + organic, data = global_data)
plot(lmr) # Looks ok
hist(lmr$residuals) # normal

lma <- glm(log(aquatics) ~ H + NO3_N + graminoids + waterDepth, data = subset(global_data, aquatics != 0))
plot(lma) # Lots of zeros
hist(lma$residuals, breaks = 20) # Heavy tailed
```

### Piecewise SEM based on mod7 - best model is mod 9
```{r}
# # Adding in year - best model!!!!!!!!!!!
# pmod7 <- psem(
#   lme(typhaBM100 ~ unVegCover + graminoids + NO3_N + organic + year, random = ~1|plot, data = global_data), 
#   lme(log(detritusAW+1) ~ waterDepth + typhaBM100, random = ~1|plot, data = global_data),
#   lme(richness ~ H + NO3_N + graminoids + typhaBM100 + organic, random = ~1|plot, data = global_data),
#   lme(log(aquatics+1) ~ H + NO3_N + graminoids + waterDepth + typhaBM100 + richness + year, random = ~1|plot, data = global_data)
# )
# summary(pmod7) # .803

pmod8 <- psem(
    lme(typhaBM100 ~ totalVegCover + year, random = ~1|plot, data = global_data),
    lme(log(detritusAW+1) ~ waterDepth + typhaBM100, random = ~1|plot, data = global_data),
    lme(richness ~ H + NO3_N + graminoids + typhaBM100 + organic, random = ~1|plot, data = global_data),
    lme(log(aquatics+1) ~ H + NO3_N + graminoids + waterDepth + typhaBM100 + richness + year, random = ~1|plot, data = global_data)
)
summary(pmod8)


#new bestest model
pmod9 <- psem(
  lme(typhaBM100 ~ totalVegCover + year, random = ~1|plot, data = global_data),
  lme(log(detritusAW+1) ~ waterDepth + typhaBM100, random = ~1|plot, data = global_data),
  lme(H ~ richness + NO3_N + graminoids + typhaBM100 + organic, random = ~1|plot, data = global_data),
  lme(log(aquatics+1) ~ H + NO3_N + graminoids + waterDepth + typhaBM100 + richness, random = ~1|plot, data = global_data)
)
summary(pmod9)
############check assumptions mod9######################
par(mfrow = c(2, 2))
lmt <- glm(typhaBM100 ~ totalVegCover + year, data = global_data)
hist(lmt$residuals, breaks = 20)# 3 outliers so normal
plot(lmt)

lmt <- glm(H ~ richness + NO3_N + graminoids + typhaBM100 + organic, data = global_data)
hist(lmt$residuals, breaks = 20)# 3 outliers so normal
plot(lmt)
```

### Global Longitudinal SEM - didn't work
```{r}

attach(long_data)
lmod1 <- 'YR2016_typhaBM100 ~ YR2015_unVegCover + YR2015_graminoids  + YR2015_typhaBM100
          YR2017_typhaBM100 ~ YR2016_graminoids + YR2016_typhaBM100
          YR2018_typhaBM100 ~ YR2017_unVegCover + YR2017_graminoids + YR2017_typhaBM100
          logYR2016_detritusAW ~ YR2015_typhaBM100 + YR2015_NH4_N + YR2015_waterDepth + logYR2015_detritusAW
          logYR2017_detritusAW ~ YR2016_typhaBM100 + YR2016_NH4_N + YR2016_waterDepth + logYR2016_detritusAW 
          logYR2018_detritusAW ~ YR2017_typhaBM100 + YR2017_NH4_N + YR2017_waterDepth + logYR2017_detritusAW  
          YR2016_richness ~ YR2015_H + YR2015_NO3_N + YR2015_graminoids + YR2015_typhaBM100 + YR2015_organic + YR2015_richness  
          YR2017_richness ~ YR2016_H + YR2016_NO3_N + YR2016_graminoids + YR2016_typhaBM100 + YR2016_organic + YR2016_richness 
          YR2018_richness ~ YR2017_H + YR2017_graminoids + YR2017_typhaBM100 + YR2017_organic + YR2017_richness 
          logYR2016_aquatics ~ YR2015_H + YR2015_NO3_N + YR2015_graminoids + YR2015_waterDepth + logYR2015_aquatics
          logYR2017_aquatics ~ YR2016_H + YR2016_NO3_N + YR2016_graminoids + YR2016_waterDepth + logYR2016_aquatics
          logYR2018_aquatics ~ YR2017_H + YR2017_graminoids + YR2017_waterDepth + logYR2017_aquatics
          YR2016_typhaBM100 ~~ logYR2016_detritusAW
          YR2016_typhaBM100 ~~ YR2016_richness
          YR2016_typhaBM100 ~~ logYR2016_aquatics
          logYR2016_detritusAW ~~ YR2016_richness
          logYR2016_detritusAW ~~ logYR2016_aquatics
          YR2016_richness ~~ logYR2016_aquatics
          YR2017_typhaBM100 ~~ logYR2017_detritusAW
          YR2017_typhaBM100 ~~ YR2017_richness
          YR2017_typhaBM100 ~~ logYR2017_aquatics
          logYR2017_detritusAW ~~ YR2017_richness
          logYR2017_detritusAW ~~ logYR2017_aquatics
          YR2017_richness ~~ logYR2017_aquatics
          YR2018_typhaBM100 ~~ logYR2018_detritusAW
          YR2018_typhaBM100 ~~ YR2018_richness
          YR2018_typhaBM100 ~~ logYR2018_aquatics
          logYR2018_detritusAW ~~ YR2018_richness
          logYR2018_detritusAW ~~ logYR2018_aquatics
          YR2018_richness ~~ logYR2018_aquatics'
modl1 = sem(lmod1, data = long_data, estimator="mlm")
summary(modl1)


lmod16 <- 'YR2016_typhaBM100 ~ YR2015_unVegCover
          logYR2016_detritusAW ~ YR2015_NH4_N + YR2015_waterDepth
          YR2016_richness ~ YR2015_H + YR2015_NO3_N + YR2015_organic
          logYR2016_aquatics ~ YR2015_H + YR2015_NO3_N + YR2015_waterDepth
          YR2016_typhaBM100 ~~ logYR2016_detritusAW
          YR2016_typhaBM100 ~~ YR2016_richness
          YR2016_typhaBM100 ~~ logYR2016_aquatics
          logYR2016_detritusAW ~~ YR2016_richness
          logYR2016_detritusAW ~~ logYR2016_aquatics
          YR2016_richness ~~ logYR2016_aquatics'
modl16 = sem(lmod16, data = long_data, estimator="mlm")
summary(modl16)
```

Best model:
pmod9 <- psem(
  lme(typhaBM100 ~ totalVegCover + year, random = ~1|plot, data = global_data),
  lme(log(detritusAW+1) ~ waterDepth + typhaBM100, random = ~1|plot, data = global_data),
  lme(H ~ richness + NO3_N + graminoids + typhaBM100 + organic, random = ~1|plot, data = global_data),
  lme(log(aquatics+1) ~ H + NO3_N + graminoids + waterDepth + typhaBM100 + richness, random = ~1|plot, data = global_data)
)



